Code Clones: To refactor or not to refactor?

### 2020-05-05 ase/paper.tex
Updates from Overleaf

For refactoring clones, we took naming the extracted method outside of the scope of the study. To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method. 
%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.

\begin{figure*}
\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
\begin{minipage}{\linewidth}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

import java.util.List;

public class GameScene
{
|\highlightYellow|	public void addToList(List l) {
|\highlightYellow|		l.add(getClass().getName());
|\highlightYellow|	}

	public int addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

import java.awt.List; // Different type

public class LoseScene
{
|\highlightYellow|	public void addToList(List l) {
|\highlightYellow|		l.add(getClass().getName());
|\highlightYellow|	}

	public String concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\end{minipage}
\end{adjustwidth}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

@@

\subsection{Ensuring equality}\label{sec:t1r}
Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}. Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code. Information that gets lost in textual comparison is the referenced declaration for type, variable and method references. Equally named type, variable and method references may refer to different declarations with a different implementation (Fig~\ref{fig:type1} shows an example of this). Such clones can be harder to refactor, if beneficial at all.

@@

% To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output. We also created a set of control projects to test the correctness for many edge cases.

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doB(a);
}
\end{javacode}}
\end{parcolumns}
\caption{A clone that spans a block partially.}
\label{fig:refactorabilitypartialblock}
\end{figure*}

@@

\subsubsection{Refactorability} \label{sec:refactorability}
Several factors may obstruct the possibility to extract code to a new method~\cite{tsantalis2015assessing}:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``Pull Up Method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CR only refactors the clones that \textit{Can Be Extracted}.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/dist2}
  \caption{Distribution of project sizes in corpus on a logarithmic scale.}
  \label{fig:dist}
\end{figure}

@@

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
}
\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
\label{tab:relation_refactor}
\end{table*}

>>>>

For refactoring clones, we took naming the extracted method outside of the scope of the study. To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.

@@

\subsection{Ensuring equality}\label{sec:t1r}
Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}. Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code. Information that gets lost in textual comparison is the referenced declaration for type, variable and method references. Equally named type, variable and method references may refer to different declarations with a different implementation. Such clones can be harder to refactor, if beneficial at all.

@@

@@

\subsubsection{Refactorability} \label{sec:refactorability}
Several factors may obstruct the possibility to extract code to a new method~\cite{tsantalis2015assessing}:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``Pull Up Method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CR only refactors the clones that \textit{Can Be Extracted}.

@@

\begin{figure}
  \includegraphics[width=1\columnwidth]{img/dist2}
  \caption{Distribution of project sizes in corpus on a logarithmic scale.}
  \label{fig:dist}
\end{figure}

@@

\begin{table*}
\centering
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
\label{tab:relation_refactor}
\end{table*}
